### 2023-11-27 documents/sections/verbs.tex
start reworking stems

\subsubsection{\rc{ka[ti]} \qu{to say}}
\label{sec:say}
This verb was not affected by any of the extensions in \PPek, \PWai, \PTir, \akuriyo, or \carijo (\crefrange{sec:pekodian}{sec:carijo}), while no first person form of its \yukpa reflex \obj{ka} is attested.
Most reflexes are simply \obj{ka}, but a fleeting syllable \rc{ti} is reconstructed by \textcite{gildea2007greenberg}, visible in the imperative forms of some languages. % \exref{kati}.
%
%\ex<kati> \apalai\\
%\obj{kaʃi-ko} \qu{say!}\\
%\parencite[35]{koehn1986apalai}
%\xe
%
\cref{tab:say} shows a comparison of the longest attested forms for each language.%
\footnote{Cognate segments in \crefrange{tab:say}{tab:bathe} were aligned automatically with LingPy \parencite{lingpy268}, for improved exposition of correspondences.
Brackets indicate segments not present in all forms.}
%
\input{floats/say.tex}%
%

>>>>

\input{floats/simple-verbs}

\subsubsection{\rc{ka[ti]} \qu{to say}}
\label{sec:say}
This verb was not affected by any of the extensions in \PPek, \PWai, \PTir, \akuriyo, \carijo, or \yukpa (\crefrange{sec:pekodian}{sec:yukpa}).
Most reflexes are simply \obj{ka}, but a fleeting second syllable \rc{ti} is reconstructed by \textcite{gildea2007greenberg}, visible in the imperative forms of some languages. % \exref{kati}.
%
%\ex<kati> \apalai\\
%\obj{kaʃi-ko} \qu{say!}\\
%\parencite[35]{koehn1986apalai}
%\xe
%
\cref{tab:say} shows a comparison of the longest attested forms for each language; brackets indicate segments not present in all forms.
%
\input{floats/say.tex}%
%
